Variational Monte Carlo on bosonic systems

### 2018-03-25 project_1/article/article.tex
Include link to source code
Reduce number of significant digits
Fix typo

\title{Variational Monte Carlo on bosonic systems}
\author{Winther-Larsen, Sebastian Gregorius}
\affiliation{University of Oslo}
\author{Schøyen, Øyvind Sigmundson}
\affiliation{University of Oslo}
\date{\today}

@@

        \begin{table}
            \centering
            \caption{One particle in one dimension for the analytic expression
            with $2^{21}$ Monte Carlo cycles and step length of $0.5$.}
            \begin{ruledtabular}
                \begin{tabular}{cccccc}
                    $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$ & $A$
                    & $t_{\text{CPU}} [\si{\second}]$ \\
                    \hline
                    0.30&0.56244&0.00026&0.00129&0.89185&0.43238\\
                    0.34&0.53652&0.00019&0.00094&0.88465&0.38340\\
                    0.38&0.51863&0.00013&0.00063&0.87844&0.37200\\
                    0.42&0.50805&0.00009&0.00038&0.87161&0.37978\\
                    0.46&0.50201&0.00004&0.00017&0.86594&0.37214\\
                    0.50&0.50000&0.00000&0.00000&0.86047&0.37162\\
                    0.54&0.50183&0.00004&0.00015&0.85543&0.37959\\
                    0.58&0.50566&0.00007&0.00029&0.84994&0.37778\\
                    0.62&0.51175&0.00011&0.00041&0.84479&0.37368\\
                    0.66&0.51906&0.00014&0.00052&0.84000&0.37257\\
                    0.70&0.52883&0.00017&0.00062&0.83570&0.37342\\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:1D1N_analytic}
        \end{table}

        \begin{table}
            \centering
            \caption{One particle in one dimension for the numeric expression
            with $2^{21}$ Monte Carlo cycles and a step length of $0.5$.}
            \begin{ruledtabular}
                \begin{tabular}{cccccc}
                    $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                    & $A$&$t_{\text{CPU}} [\si{\second}]$ \\
                    \hline
                    0.30&0.56675&0.00026&0.00135&0.89098&0.52634\\
                    0.34&0.53714&0.00019&0.00096&0.88479&0.52186\\
                    0.38&0.51836&0.00013&0.00062&0.87820&0.52351\\
                    0.42&0.50717&0.00009&0.00038&0.87180&0.52892\\
                    0.46&0.50184&0.00004&0.00017&0.86581&0.51759\\
                    0.50&0.50000&0.00001&0.00001&0.86024&0.52427\\
                    0.54&0.50133&0.00004&0.00015&0.85520&0.52052\\
                    0.58&0.50520&0.00007&0.00028&0.84971&0.52156\\
                    0.62&0.51120&0.00011&0.00039&0.84481&0.51830\\
                    0.66&0.51896&0.00014&0.00052&0.83990&0.51865\\
                    0.70&0.52794&0.00017&0.00061&0.83506&0.51255\\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:1D1N_numeric}
        \end{table}

@@

        Systems of optimum variational parameter warrants further investigation,
        as summed up in \autoref{tab:initial_optimum_comparison}. The analytical
        results are quite predictable and monotonous; the expected local energy
        $\expval{E_l}$ is perfectly proportional by a factor $\frac{3}{2}$ to
        the number of particles and the standard deviation $\sigma_b$ is zero
        for systems of any number of particles. The numerical results tells a
        more tortuous tale. As the number of particles increase, the uncertainty
        also increases rapidly. For the largest system, with $N = 500$
        particles, the energy misses its target critically - the true energy is
        more than one standard deviation away. Lastly, the cpu time is notably
        higher for the numeric scheme.

@@

            \begin{table}
                \caption{Importance sampled simulations of $n=10$ particles in
                $d=3$ dimensions. Average acceptance ratios and standard
                deviations for eleven alpha values between $0.3$ and $0.7$.}
                \centering
                    \begin{ruledtabular}
                        \begin{tabular}{cccc}
                            $\delta t$ & $\bar{\sigma}_b$ & $\bar{A}$
                            & $\expval{E}\left(\alpha = \frac{1}{2}\right)$ \\
                            \hline
                            $2^{+3}$ & 0.09363 & 0.00531 & 15.000 \\
                            $2^{+2}$ & 0.01549  & 0.04123 & 15.000 \\
                            $2^{+1}$ & 0.00706 & 0.21604 & 15.000 \\
                            $2^{\ 0}$ & 0.00675 & 0.51030 & 15.000 \\
                            $2^{-1}$ & 0.00932 & 0.73779 & 15.000 \\
                            $2^{-2}$ & 0.01578 & 0.86633 & 15.000 \\
                            $2^{-3}$ & 0.02723 & 0.93305 & 15.000 \\
                            $2^{-4}$ & 0.05016 & 0.96654 & 15.000 \\
                            $2^{-5}$ & 0.08474 & 0.98316 & 15.000 \\
                            $2^{-6}$ & 0.11555 & 0.99174 & 15.000 \\
                            $2^{-7}$ & 0.17070 & 0.99612 & 15.000 \\
                        \end{tabular}
                    \end{ruledtabular}
                    \label{tab:imp_time_step}
            \end{table}

>>>>

\title{Variational Monte Carlo on bosonic systems}
\author{Winther-Larsen, Sebastian Gregorius}
\homepage[Project code: ]{https://github.com/Schoyen/FYS4411}
\affiliation{University of Oslo}
\author{Schøyen, Øyvind Sigmundson}
\homepage[Project code: ]{https://github.com/Schoyen/FYS4411}
\affiliation{University of Oslo}
\date{\today}

@@

        \begin{table}
            \centering
            \caption{One particle in one dimension for the analytic expression
            with $2^{21}$ Monte Carlo cycles and step length of $0.5$.}
            \begin{ruledtabular}
                \begin{tabular}{cccccc}
                    $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                    & $A$ & $t_{\text{CPU}} [\si{\second}]$ \\
                    \hline
                    0.30&0.56244&0.00026&0.00129&0.892&0.43\\
                    0.34&0.53652&0.00019&0.00094&0.885&0.38\\
                    0.38&0.51863&0.00013&0.00063&0.878&0.37\\
                    0.42&0.50805&0.00009&0.00038&0.872&0.38\\
                    0.46&0.50201&0.00004&0.00017&0.866&0.37\\
                    0.50&0.50000&0.00000&0.00000&0.860&0.37\\
                    0.54&0.50183&0.00004&0.00015&0.855&0.38\\
                    0.58&0.50566&0.00007&0.00029&0.850&0.38\\
                    0.62&0.51175&0.00011&0.00041&0.845&0.37\\
                    0.66&0.51906&0.00014&0.00052&0.840&0.37\\
                    0.70&0.52883&0.00017&0.00062&0.836&0.37\\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:1D1N_analytic}
        \end{table}

        \begin{table}
            \centering
            \caption{One particle in one dimension for the numeric expression
            with $2^{21}$ Monte Carlo cycles and a step length of $0.5$.}
            \begin{ruledtabular}
                \begin{tabular}{cccccc}
                    $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                    & $A$&$t_{\text{CPU}} [\si{\second}]$ \\
                    \hline
                    0.30&0.56675&0.00026&0.00135&0.891&0.53\\
                    0.34&0.53714&0.00019&0.00096&0.885&0.52\\
                    0.38&0.51836&0.00013&0.00062&0.878&0.52\\
                    0.42&0.50717&0.00009&0.00038&0.872&0.53\\
                    0.46&0.50184&0.00004&0.00017&0.866&0.52\\
                    0.50&0.50000&0.00001&0.00001&0.860&0.52\\
                    0.54&0.50133&0.00004&0.00015&0.855&0.52\\
                    0.58&0.50520&0.00007&0.00028&0.850&0.52\\
                    0.62&0.51120&0.00011&0.00039&0.845&0.52\\
                    0.66&0.51896&0.00014&0.00052&0.840&0.52\\
                    0.70&0.52794&0.00017&0.00061&0.835&0.51\\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:1D1N_numeric}
        \end{table}

@@

        Systems of optimum variational parameter warrants further investigation,
        as summed up in \autoref{tab:initial_optimum_comparison}. The analytical
        results are quite predictable and monotonous; the expected local energy
        $\expval{E_L}$ is perfectly proportional by a factor $\frac{3}{2}$ to
        the number of particles and the standard deviation $\sigma_b$ is zero
        for systems of any number of particles. The numerical results tells a
        more tortuous tale. As the number of particles increase, the uncertainty
        also increases rapidly. For the largest system, with $N = 500$
        particles, the energy misses its target critically - the true energy is
        more than one standard deviation away. Lastly, the cpu time is notably
        higher for the numeric scheme.

@@

            \begin{table}
                \caption{Importance sampled simulations of $n=10$ particles in
                $d=3$ dimensions. Average acceptance ratios and standard
                deviations for eleven alpha values between $0.3$ and $0.7$.}
                \centering
                    \begin{ruledtabular}
                        \begin{tabular}{cccc}
                            $\delta t$ & $\bar{\sigma}_b$ & $\bar{A}$
                            & $\expval{E}\left(\alpha = 1/2\right)$ \\
                            \hline
                            $2^{+3}$ & 0.09363 & 0.005 & 15.000 \\
                            $2^{+2}$ & 0.01549  & 0.041 & 15.000 \\
                            $2^{+1}$ & 0.00706 & 0.216 & 15.000 \\
                            $2^{\ 0}$ & 0.00675 & 0.510 & 15.000 \\
                            $2^{-1}$ & 0.00932 & 0.738 & 15.000 \\
                            $2^{-2}$ & 0.01578 & 0.866 & 15.000 \\
                            $2^{-3}$ & 0.02723 & 0.933 & 15.000 \\
                            $2^{-4}$ & 0.05016 & 0.966 & 15.000 \\
                            $2^{-5}$ & 0.08474 & 0.983 & 15.000 \\
                            $2^{-6}$ & 0.11555 & 0.992 & 15.000 \\
                            $2^{-7}$ & 0.17070 & 0.996 & 15.000 \\
                        \end{tabular}
                    \end{ruledtabular}
                    \label{tab:imp_time_step}
            \end{table}
